---
title: "Comparison of NMFS survey results from `crabpack` with the 2024 Tanner crab assessment"
author: "William T. Stockhausen"
institute: NOAA/NMFS/AFSC
date: '`r format(Sys.time(), "%b %e, %Y")`'
fontsize: 11pt 
number-sections: true
reference-location: document
bibliography: '`r path.expand("~/Work/Projects/Bibliography/AllRefs.bib")`'
csl: '`r system.file("files/CJFAS.csl",package="wtsQMD")`'
link-citations: true
crossref:
  chapters: false      # prepend label reference numbers by chater number?
  fig-title: Figure    # for caption: default is "Figure")
  tbl-title: Table     # for caption: default is "Table")
  title-delim: "."     # for caption: default is ":")
  fig-prefix: Figure   # for in-text (use [-@fig-ref] to drop prefix in text)
  tbl-prefix: Table    # for in-text (use [-@tbl-ref] to drop prefix in text)
  fig-labels: arabic    # options are arabic, roman, roman i, alpha x, alpha X; latter two starting from x/X
  tbl-labels: arabic    # options are arabic, roman, roman i, alpha x, alpha X; latter two starting from x/X
  subref-labels: alpha a # options are arabic, roman, roman i, alpha x, alpha X; latter two starting from x/X
  ref-hyperlink: true    # references are hyperlinked if true
format: 
  html: 
    df-print: paged
    toc: true
    toc-location: right
    fig-width: 8
    fig-asp: 1.4
    fig-dpi: 100
    embed-resources: true
    include-in-header: 
      - '`r system.file("files/in-line_math_mode.html",package="wtsQMD")`'
  pdf:
    documentclass: scrartcl
    toc: false
    fig_crop: false
    keep-tex: false
    geometry:
      - left=1.0in
      - right=1.0in
      - top=1.0in
      - bottom=1.0in
      - textwidth=6.5in
      - showframe=false
    include-in-header: 
      - text: |
          \usepackage{placeins}
          \extrafloats{500}
          \maxdeadcycles=10000
      - file: '`r system.file("files/ltx_ExtraLatexIncludes.tex",package="wtsQMD")`'
echo: false
warning: false
results: 'hide'
keep-md: false
keep-yaml: false
editor: source
editor_options: 
  chunk_output_type: console
concordance: true
params:
  setup: !expr 'system.file("files/qmd_setup.R",package="wtsQMD")'
  dirAsmt: "~/Work/StockAssessments-Crab/Assessments/TannerCrab/2024-09_TannerCrab/AssessmentData/Data_Surveys_NMFS"
  testing: false
---
<!-- IMPORTANT: if used as a child doc, all chunk labels must be unique within the overall document -->

<!-- 
  NOTEs: 
     * child_path$peek() gives path to current script.
     * before starting a child document, do 
         "child_path$push(file.path(child_path$peek(),rel_path))" first, 
         where rel_path is the relative path to the child
     * after a child document has finished, do "child_path$pop()" to return to current path value
-->

<!-- if not child doc, set up required objects -->
```{r}
#| label: SurveyData_setup
#| eval: !expr '!knitr::opts_knit$get("child")'
#| results: "asis"
  testing = params$testing;
  if (testing) cat(params$setup,"\n\n")
  source(params$setup);
  if (testing) cat("root = ",root,"\n\n")
```

```{r}
#| label: setup_SurveyData
#| results: 'asis'
  require(crabpack);
  require(ggplot2);
  require(kableExtra);
  require(tables);

  #--constants
  MILLION  = 1000000;
  THOUSAND = 1000;

  #--survey years to include
  yrs = 1975:2024;
```

```{r getSurveyData}
  dirTC = params$dirAsmt;
  lstTC = wtsUtilities::getObj(file.path(dirTC,"rda_SrvData.NMFS.DBI.RData"));
  
  #--Tanner crab data for crabpack----
  #----old: lstCP = readRDS("./EBS_specimen/tanner_specimen_2024.rds");
  if (FALSE){
    lstCP = get_specimen_data(species="TANNER",
                              region="EBS",
                              district="ALL",
                              channel="API");
    wtsUtilities::saveObj(lstCP,"rda_crabpack_specimen_data.TannerCrab.RData");
  } else {
    lstCP = wtsUtilities::getObj("rda_crabpack_specimen_data.TannerCrab.RData");
  }
```

```{r calcSurveyABs}
  #--Biomass and abundance----
  ##--get TCSAM02 biomass/abundance time series
  dfrT_ABs = lstTC$lstABs$ABs$EBS |> 
                dplyr::select(y=YEAR,x=SEX,m=MATURITY,
                              abd=totABUNDANCE,abdCV=cvABUNDANCE,
                              bio=totBIOMASS,bioCV=cvBIOMASS) |> 
                dplyr::mutate(type="asmt",
                              abd=MILLION*abd,  #--convert from millions to ones
                              bio=THOUSAND*bio);#--convert from 1,000's t to t
  
  ##--get crabpack biomass/abundance time series----
  dfrC_ABMs = calc_bioabund(lstCP,
                          species="TANNER",
                          region="EBS",
                          years=1975:2024,
                          sex="male",
                          size_min=24.5,
                          spatial_level="region") |> 
          dplyr::select(y=YEAR,
                        abd=ABUNDANCE,abdCV=ABUNDANCE_CV,
                        bio=BIOMASS_MT,bioCV=BIOMASS_MT_CV) |> 
          dplyr::mutate(x="MALE",m="UNDETERMINED",type="crabpack");
  #head(dfrC_ABMs);
  dfrC_ABFIs = calc_bioabund(lstCP,
                          species="TANNER",
                          region="EBS",
                          years=1975:2024,
                          sex="female",
                          crab_category="immature_female",
                          female_maturity="morphometric",
                          size_min=24.5,
                          spatial_level="region") |> 
                dplyr::select(y=YEAR,
                              abd=ABUNDANCE,abdCV=ABUNDANCE_CV,
                              bio=BIOMASS_MT,bioCV=BIOMASS_MT_CV) |> 
                dplyr::mutate(x="FEMALE",m="IMMATURE",type="crabpack");
  #head(dfrC_ABFIs);
  dfrC_ABFMs = calc_bioabund(lstCP,
                          species="TANNER",
                          region="EBS",
                          years=1975:2024,
                          sex="female",
                          crab_category="mature_female",
                          female_maturity="morphometric",
                          size_min=24.5,
                          spatial_level="region") |> 
                dplyr::select(y=YEAR,
                              abd=ABUNDANCE,abdCV=ABUNDANCE_CV,
                              bio=BIOMASS_MT,bioCV=BIOMASS_MT_CV) |> 
                dplyr::mutate(x="FEMALE",m="MATURE",type="crabpack");
  #head(dfrC_ABFMs);
  ##--combine datafraames
  dfrABs = dplyr::bind_rows(dfrT_ABs,dfrC_ABMs,dfrC_ABFIs,dfrC_ABFMs);
  #head(dfrABs);

  #--calculate differences in abundance
  dfrAsp = dfrABs |> dplyr::select(y,x,m,abd,type) |> 
              tidyr::pivot_wider(names_from="type",values_from="abd") |> 
              dplyr::mutate(diff=asmt-crabpack,
                            pdif=2*100*diff/(asmt+crabpack));
  #--calculate differences in biomass
  dfrBsp = dfrABs |> dplyr::select(y,x,m,bio,type) |> 
              tidyr::pivot_wider(names_from="type",values_from="bio") |> 
              dplyr::mutate(diff=asmt-crabpack,
                            pdif=2*100*diff/(asmt+crabpack));
```

## Introduction

The ASFC's Shellfish Assessment Program has introduced `crabpack`, a new R package [@ref-R] to access NMFS EBS crab survey data and subsequently estimate annual abundance, biomass, and size compositions by year for several population categories (e.g., sex, maturity state). The [tcsamSurveyData](https://github.com/wStockhausen/tcsamSurveyData) R package has been used previously with survey haul data files downloaded from [AKFIN](https://akfin.psmfc.org) Answers to provide similar information for the Tanner crab assessment [e.g., @TannerCrab2024]. Here, the two approaches are compared for EBS-wide abundance, biomass, and size compositions for NMFS EBS crab survey data from 1975 to 2024.

## Survey abundance estimates

Estimates of EBS-wide abundance from the NMFS bottom trawl survey for male and female Tanner crab by maturity state are compared by year in [@fig-SrvAbd] for calculations made in the 2024 assessment [@TannerCrab2024] and with the `crabpack` R package. Absolute differences and percent differences between the two methods are shown, respectively, in Figures [-@fig-SrvAbdAbsDif] and [-@fig-SrvAbdPctDif]. The percent differences are also shown in Table [-@tbl-SrvAbdPctDif] to two decimal places. The figures and table show excellent agreement between the two methods in all survey years except 1979, when estimates from the two methods differ substantially (> 10%). The estimates from the assessment are less than those from `crabpack` in 1979. The differences in the two methods apparently reflect differences in the hauls included in the calculation (`crabpack` appears to include hauls at corner stations that were only conducted in 1979, while these were excluded in the standardized time series used in the assessment).

```{r}
#| label: fig_SrvAbd
#| results: asis
#| fig-width: 6.5
#| fig-asp: 1.25
  p1 = ggplot(dfrABs |> dplyr::mutate(abd=abd/1000000,xm=tolower(paste(m,x))),
              aes(x=y,y=abd,ymin=abd*(1-abdCV),ymax=abd*(1+abdCV),colour=type,fill=type,shape=type)) + 
       geom_ribbon(alpha=0.3,colour=NA) + geom_line() + geom_point(fill=NA,size=3) + 
       scale_fill_manual(values=c("gold","blue"),aesthetics=c("colour","fill")) + 
       scale_shape_manual(values=c(24,25)) + 
       facet_grid(xm~.) + 
       labs(y="Abundance (millions)") + 
       wtsPlots::getStdTheme() + 
       theme(axis.title.x=element_blank(),
             legend.title=element_blank(),
             legend.position="inside",
             legend.position.inside=c(0.99,0.99),
             legend.justification=c(1,1));
  cap = paste0("Comparison of annual estimates of design-based area-swept abundance ",
               "from the NMFS EBS bottom trawl survey by the 2024 assessment (*asmt*) and ",
               "the `crabpack` R package (*crabpack*), by sex and maturity state.");
  lbl = wtsQMD::getLabel();
  pth = wtsQMD::getFigFN();
  lstFigs = c(lstFigs,wtsQMD::printGGplot(p1,lbl=lbl,cap=cap,pth=pth,ori="P"));
```

```{r}
#| label: fig_SrvAbdAbsDif
#| results: asis
#| fig-width: 6.5
#| fig-asp: 1.25
p1 = ggplot(dfrAsp |> dplyr::mutate(diff=diff/MILLION,xm=tolower(paste(m,x))),
            aes(x=y,y=diff)) + 
     geom_line() + geom_point(fill=NA,size=3) + 
     geom_hline(yintercept=0,linetype=3) + 
     scale_fill_manual(values=c("gold","blue"),aesthetics=c("colour","fill")) + 
     scale_shape_manual(values=c(24,25)) + 
     facet_grid(xm~.) + 
     labs(y="Abundance Difference (millions)") + 
     wtsPlots::getStdTheme() + 
     theme(axis.title.x=element_blank(),
           legend.title=element_blank(),
           legend.position="inside",
           legend.position.inside=c(0.99,0.99),
           legend.justification=c(1,1));
  cap = paste0("Differences in annual estimates of design-based area-swept abundance ",
               "from the NMFS EBS bottom trawl survey by the 2024 assessment and ",
               "the `crabpack` R package, by sex and maturity state.");
  lbl = wtsQMD::getLabel();
  pth = wtsQMD::getFigFN();
  lstFigs = c(lstFigs,wtsQMD::printGGplot(p1,lbl=lbl,cap=cap,pth=pth,ori="P"));
```

```{r}
#| label: fig_SrvAbdPctDif
#| results: asis
#| fig-width: 6.5
#| fig-asp: 1.25
p2 = ggplot(dfrAsp |> dplyr::mutate(xm=tolower(paste(m,x))),
            aes(x=y,y=pdif)) + 
     geom_line() + geom_point(fill=NA,size=3) + 
     geom_hline(yintercept=0,linetype=3) + 
     scale_fill_manual(values=c("gold","blue"),aesthetics=c("colour","fill")) + 
     scale_shape_manual(values=c(24,25)) + 
     facet_grid(xm~.) + 
     labs(y="% Difference in Abundance") + 
     wtsPlots::getStdTheme() + 
     theme(axis.title.x=element_blank(),
           legend.title=element_blank(),
           legend.position="inside",
           legend.position.inside=c(0.99,0.99),
           legend.justification=c(1,1));
  cap = paste0("Percent differences in annual estimates of design-based area-swept abundance ",
               "from the NMFS EBS bottom trawl survey by the 2024 assessment and ",
               "the `crabpack` R package, by sex and maturity state.");
  lbl = wtsQMD::getLabel();
  pth = wtsQMD::getFigFN();
  lstFigs = c(lstFigs,wtsQMD::printGGplot(p2,lbl=lbl,cap=cap,pth=pth,ori="P"));
```

```{r tbl.SrvAbdPctDif}
#| results: asis
  tblr = tabular(Factor(y,name="year") ~ Factor(xm)*pdif*mean,
                 data=dfrAsp |> dplyr::mutate(xm=tolower(paste(m,x)),
                                               pdif=round(pdif,1)));
  colLabels(tblr) = colLabels(tblr)[2,];
  kblr = tblr |> wtsQMD::convert_tblr_to_kbl(col_spec=c(1),!isPDF,
                                             ltx_font_size=7,replaceNAs="--",adjColSpacing=-4);
  cap = paste0("Percent difference, by year, in  design-based NMFS survey abundance trends ",
               "from the 2024 assessment and the `crabpack` R package, by sex and maturity state.");
  lstTbls = c(lstTbls,
              wtsQMD::insertKblIntoQMD(kblr,
                                       lbl="tbl-SrvAbdPctDif", 
                                       cap=cap,
                                       ori="P"));
  rm(tblr,kblr,cap);
```

## Survey biomass estimates

Estimates of EBS-wide biomass from the NMFS bottom trawl survey for male and female Tanner crab by maturity state are compared by year in [@fig-SrvBio] for calculations made in the 2024 assessment [@TannerCrab2024] and with the `crabpack` R package. Absolute differences and percent differences between the two methods are shown, respectively, in Figures [-@fig-SrvBioAbsDif] and [-@fig-SrvBioPctDif]. The percent differences are also shown in Table [-@tbl-SrvBioPctDif] to two decimal places. 

As with abundance, the figures and table demonstrate excellent agreement between the two methods in all survey years prior to 2016 except 1979, when estimates from the two methods differ substantially (> 10%). Unlike the abundance estimates, the two methods also exhibit small differences (< 5 %) in 2016 and subsequent years. The estimates from the assessment for 2016 and later are larger than those from `crabpack` in all years. The post-2015 differences between the two methods may reflect differences in the size used to calculate the weight of individual crab: the assessment uses carapace width to the first decimal place while `crabpack` apparently uses the carapace width to 1-mm.

```{r}
#| label: fig_SrvBio
#| results: asis
#| fig-width: 6.5
#| fig-asp: 1.25
  p1 = ggplot(dfrABs |> dplyr::mutate(bio=bio/THOUSAND,xm=tolower(paste(m,x))),
              aes(x=y,y=bio,ymin=bio*(1-bioCV),ymax=bio*(1+bioCV),colour=type,fill=type,shape=type)) + 
       geom_ribbon(alpha=0.3,colour=NA) + geom_line() + geom_point(fill=NA,size=3) + 
       scale_fill_manual(values=c("gold","blue"),aesthetics=c("colour","fill")) + 
       scale_shape_manual(values=c(24,25)) + 
       facet_grid(xm~.,scales="free_y") + 
       labs(y="Biomass (1000's t)") + 
       wtsPlots::getStdTheme() + 
       theme(axis.title.x=element_blank(),
             legend.title=element_blank(),
             legend.position="inside",
             legend.position.inside=c(0.99,0.99),
             legend.justification=c(1,1));
  cap = paste0("Comparison of annual estimates of design-based area-swept biomass ",
               "from the NMFS EBS bottom trawl survey by the 2024 assessment (*asmt*) and ",
               "the `crabpack` R package (*crabpack*), by sex and maturity state.");
  lbl = wtsQMD::getLabel();
  pth = wtsQMD::getFigFN();
  lstFigs = c(lstFigs,wtsQMD::printGGplot(p1,lbl=lbl,cap=cap,pth=pth,ori="P"));
```

```{r}
#| label: fig_SrvBioAbsDif
#| results: asis
#| fig-width: 6.5
#| fig-asp: 1.25
p1 = ggplot(dfrBsp |> dplyr::mutate(diff=diff/THOUSAND,xm=tolower(paste(m,x))),
            aes(x=y,y=diff)) + 
     geom_line() + geom_point(fill=NA,size=3) + 
     geom_hline(yintercept=0,linetype=3) + 
     scale_fill_manual(values=c("gold","blue"),aesthetics=c("colour","fill")) + 
     scale_shape_manual(values=c(24,25)) + 
     facet_grid(xm~.) + 
     labs(y="Biomass Difference (1,000's t)") + 
     wtsPlots::getStdTheme() + 
     theme(axis.title.x=element_blank(),
           legend.title=element_blank(),
           legend.position="inside",
           legend.position.inside=c(0.99,0.99),
           legend.justification=c(1,1));
  cap = paste0("Differences in annual estimates of design-based area-swept biomass ",
               "from the NMFS EBS bottom trawl survey by the 2024 assessment and ",
               "the `crabpack` R package, by sex and maturity state.");
  lbl = wtsQMD::getLabel();
  pth = wtsQMD::getFigFN();
  lstFigs = c(lstFigs,wtsQMD::printGGplot(p1,lbl=lbl,cap=cap,pth=pth,ori="P"));
```

```{r}
#| label: fig_SrvBioPctDif
#| results: asis
#| fig-width: 6.5
#| fig-asp: 1.25
p2 = ggplot(dfrBsp |> dplyr::mutate(xm=tolower(paste(m,x))),
            aes(x=y,y=pdif)) + 
     geom_line() + geom_point(fill=NA,size=3) + 
     geom_hline(yintercept=0,linetype=3) + 
     scale_fill_manual(values=c("gold","blue"),aesthetics=c("colour","fill")) + 
     scale_shape_manual(values=c(24,25)) + 
     facet_grid(xm~.) + 
     labs(y="% Difference in Biomass") + 
     wtsPlots::getStdTheme() + 
     theme(axis.title.x=element_blank(),
           legend.title=element_blank(),
           legend.position="inside",
           legend.position.inside=c(0.99,0.99),
           legend.justification=c(1,1));
  cap = paste0("Percent differences in annual estimates of design-based area-swept biomass ",
               "from the NMFS EBS bottom trawl survey by the 2024 assessment and ",
               "the `crabpack` R package, by sex and maturity state.");
  lbl = wtsQMD::getLabel();
  pth = wtsQMD::getFigFN();
  lstFigs = c(lstFigs,wtsQMD::printGGplot(p2,lbl=lbl,cap=cap,pth=pth,ori="P"));
```

```{r tbl.SrvBioPctDif}
#| results: asis
  tblr = tabular(Factor(y,name="year") ~ Factor(xm)*pdif*mean,
                 data=dfrBsp |> dplyr::mutate(xm=tolower(paste(m,x)),
                                               pdif=round(pdif,1)));
  colLabels(tblr) = colLabels(tblr)[2,];
  kbl = tblr |> wtsQMD::convert_tblr_to_kbl(col_spec=c(1),isHTM,
                                            ltx_font_size=7,replaceNAs="--",adjColSpacing=-4);
  cap = paste0("Percent difference, by year, in  design-based NMFS survey biomass trends ",
               "from the 2024 assessment and the `crabpack` R package, by sex and maturity state.");
  lstTbls = c(lstTbls,
              wtsQMD::insertKblIntoQMD(kbl,
                                       lbl="tbl-SrvBioPctDif", 
                                       cap=cap,
                                       ori="P"));
  rm(tblr,kbl,cap);
```

<!-- references, if not child doc -->
```{r,eval=!knitr::opts_knit$get("child"),results='asis'}
  cat("# References {-}\n");
  cat("::: {#refs}\n");
  cat(":::\n\n");
```

<!-- tables, if not child doc and lstTbls is not empty -->
```{r}
#| label: tables_SrvData
#| eval: !expr '!knitr::opts_knit$get("child")'
#| results: asis
  source(system.file("files/printTablesSectionFromList.R",package="wtsQMD"));
```

<!-- figures, if not child doc and lstFigs is not empty -->
```{r}
#| label: figures_SrvData
#| eval: !expr '!knitr::opts_knit$get("child")'
#| results: asis
  source(system.file("files/printFiguresSectionFromList.R",package="wtsQMD"));
```
