---
title: "Estimated Fishery-related Quantities"
author: William T. Stockhausen
affiliation: NOAA/NMFS/AFSC
date: '`r format(Sys.time(), "%b %e, %Y")`'
fontsize: 11pt 
number-sections: true
reference-location: document
bibliography: '`r path.expand("~/Work/Projects/Bibliography/AllRefs.bib")`'
csl: '`r system.file("files/CJFAS.csl",package="wtsQMD")`'
crossref:
  chapters: false      # prepend label reference numbers by chater number?
  fig-title: Figure    # for caption: default is "Figure")
  tbl-title: Table     # for caption: default is "Table")
  title-delim: "."     # for caption: default is ":")
  fig-prefix: Figure   # for in-text (use [-@fig-ref] to drop prefix in text)
  tbl-prefix: Table    # for in-text (use [-@tbl-ref] to drop prefix in text)
  fig-labels: arabic    # options are arabic, roman, roman i, alpha x, alpha X; latter two starting from x/X
  tbl-labels: arabic    # options are arabic, roman, roman i, alpha x, alpha X; latter two starting from x/X
  subref-labels: alpha a # options are arabic, roman, roman i, alpha x, alpha X; latter two starting from x/X
  ref-hyperlink: true    # references are hyperlinked if true
format: 
  html: 
    df-print: paged
    toc: true
    toc-location: right
    fig-width: 6.5
    fig-asp: 0.6
    fig-dpi: 100
    embed-resources: true
    include-in-header: 
      - '`r system.file("files/in-line_math_mode.html",package="wtsQMD")`'
  pdf:
    documentclass: scrartcl
    toc: false
    fig_crop: false
    keep-tex: false
    fig-width: 6.5
    fig-asp: 0.6
    fig-dpi: 100
    geometry:
      - left=1.0in
      - right=1.0in
      - top=1.0in
      - bottom=1.0in
      - textwidth=6.5in
      - showframe=false
    include-in-header: 
      - text: |
          \usepackage{placeins}
          \extrafloats{500}
          \maxdeadcycles=10000
          \usepackage{fontspec}
          \usepackage{multicol}
          \usepackage{hhline}
          \newlength\Oldarrayrulewidth
          \newlength\Oldtabcolsep
      - file: '`r system.file("files/ltx_ExtraLatexIncludes.tex",package="wtsQMD")`'
echo: false
warning: false
results: 'hide'
keep-md: false
keep-yaml: false
editor: source
editor_options: 
  chunk_output_type: console
concordance: true
params:
  setup: !expr 'system.file("files/qmd_setup.R",package="wtsQMD")'
  testing: false
---

<!-- if not child doc, set up required objects -->
```{r}
#| label: TCSAM02Mods-FshQtys_setup
#| eval: !expr '!knitr::opts_knit$get("child")'
#| results: "asis"
  if (!exists("testing")) testing = params$testing;
  if (testing) cat(params$setup,"\n\n")
  source(params$setup);
  if (testing) {
    cat("In TCSAM02Mods-FshQtys_setup:\n\n")
    cat("root = ",root,"\n\n");
    cat("peek = '",child_path$peek(),"'\n\n",sep="");
  }
```

```{r}
#| label: setup_TCSAM02Mods-FshQtys
#| results: 'asis'
  require(ggplot2);
  require(kableExtra);
  require(rCompTCMs);
  require(tables);
  require(wtsQMD);
  Sum = wtsUtilities::Sum;
  old_thm = ggplot2::theme_set(cowplot::theme_cowplot(font_size = 10) +
                               cowplot::background_grid() +
                               cowplot::panel_border());
  thm = wtsPlots::getStdTheme();
  options("readr.show_col_types"=FALSE);
  if (testing) cat("dirThs =",child_path$peek(),"\n\n")
  # if (!exists("s")){
  #   fn = ifelse(child_path$peek()!="",
  #               file.path(child_path$peek(),"../..",params$rdaAsmtSetup),
  #               file.path(rstudioapi::getActiveProject(),
  #                         params$rdaAsmtSetup));
  #   s = wtsUtilities::getObj(fn);
  # }
  dirThs = child_path$peek();                #--path to "this" folder
  dirPrj = file.path(child_path$peek(),"..");#--path to project folder from "this" folder
  if (!exists("models"))
    models = wtsUtilities::getObj(file.path(dirThs,"rda_Models.RData"));

  if (!exists("asmtYr")) asmtYr = 2024;

  if (!exists("strAY"))  strAY  = wtsQMD::crabYear(asmtYr);
  if (!exists("currYr")) currYr = wtsQMD::crabYear(asmtYr-1);#--current fishery year

  prvYr = asmtYr-1;
  if (!exists("tblno")) tblno = 0;#--index in LETTERS for tables in text
```

```{r}
  prvMod = "22.03d5";#--previous assessment model
  compare  = names(models);
  cases1   = compare;
  cases2   = NULL;
  obs_case = prvMod;
  if (!exists("PLOT_OBJECTS")){
    #--PLOT OBJECTS---------------------------------------
    source(file.path(dirThs,"../RCode_Markdown/r_FigureFunctions.R"));
    std_theme = wtsPlots::getStdTheme();
    ggT = ggplot2::theme(plot.title=element_text(size=10,margin=margin()),
                         panel.spacing = grid::unit(0.01,"in"),
                         legend.position="none", 
                         plot.margin=margin(0,0,0,1));
    ggL = labs(title=NULL,subtitle=NULL);
    noL  = theme(legend.position="none");
    noXT = theme(axis.title.x=element_blank());
    colour_scale=ggplot2::scale_color_hue();
    fill_scale  =ggplot2::scale_fill_hue();
    PLOT_OBJECTS = "PLOT_OBJECTS";#--make flag to prevent doing this again
  }
```

## Estimated Fishery-related Quantities {#sec-TCSAM02FshQtys}

All estimated fishery-related quantities are essentially identical for all of the models.
Graphs of time series of estimated fully-selected F (total catch capture rates, not necessarily mortality) in the directed fishery are shown in Figure [-@fig-TCSAM02Mods-FshQtys-TCF-CRs], while the associated selectivity functions are illustrated in Figures [-@fig-TCSAM02Mods-FshQtys-TCF-SelFcnsF]-[-@fig-TCSAM02Mods-FshQtys-TCF-SelFcnsM2]. The estimates of size-selective retention of males captured in the directed fishery are presented in Figure [-@fig-TCSAM02Mods-FshQtys-TCF-RetFcns]. Graphs of time series of estimated fully-selected F (again, total catch capture rates, not mortality) and the associated selectivity functions for the bycatch fisheries are shown in Figures [-@fig-TCSAM02Mods-FshQtys-SCF-CRs]-[-@fig-TCSAM02Mods-FshQtys-GFAll-CRs].

```{r }
#| label: fig_TCSAM02Mods-FshQtys
#| fig-asp: 1.23
#| results: asis
  #--directed fishery----
  fleet_="TCF";
  ##--fully-selected capture rates----
  ps1 = rCompTCMs::compareResults.Fisheries.Catchability(models[compare],
                                                         fleets=fleet_,
                                                         cast="x",
                                                         facet_grid=x~.,
                                                         years="all");
  ps2 = rCompTCMs::compareResults.Fisheries.Catchability(models[compare],
                                                         fleets=fleet_,
                                                         cast="x",
                                                         facet_grid=x~.,
                                                         years=1980:asmtYr);
  lg = cowplot::get_legend(ps2[[1]]);
  pg1 = cowplot::plot_grid(ps1[[1]]+noXT+noL+ggL,
                           ps2[[1]]+noXT+noL+ggL,ncol=1); 
  pg2 = cowplot::plot_grid(pg1,lg,nrow=1,rel_widths=c(8,1));
  cap = paste0("TCSAM02 models estimated fully-selected capture rates (not mortality) in the directed fishery. ",
               "The lower pair of plots show the estimated time series since 1980. ");
  xt  = paste0("-TCF-CRs");
  lbl = wtsQMD::getLabel(xt);
  pth = wtsQMD::getFigFN(xt);
  lstFigs = c(lstFigs,wtsQMD::printGGplot(pg2,lbl=lbl,cap=cap,pth=pth,ori="P"));
  rm(ps1,ps2,lg,pg1,pg2,cap,xt,lbl,pth);

  #----selectivity functions----
  mdfr1 = rCompTCMs::extractMDFR.Fisheries.SelFcns(models[compare],
                                                        fleets=fleet_,
                                                        cast="y+x",
                                                        years=c(1990:2021));

  # ##--females----
  # p1 = ggplot(mdfr1 %>% dplyr::filter(x=="female",y==1990) |> dplyr::mutate(block="all years"),
  #             aes(x=z,y=val,colour=case,shape=case)) +
  #        geom_line() + geom_point() +
  #        facet_wrap(~block) +
  #        labs(x="Size (mm CW)",y="selectivity") +
  #        wtsPlots::getStdTheme(); if (testing) print(p1);
  # cap = paste0("TCSAM02 models estimated selectivity for females in the directed fishery for all years.");
  # xt  = paste0("-TCF-SelFcnsF");
  # lbl = wtsQMD::getLabel(xt);
  # pth = wtsQMD::getFigFN(xt);
  # lstFigs = c(lstFigs,wtsQMD::printGGplot(p1,lbl=lbl,cap=cap,pth=pth,asp=0.5,ori="P"));
  # 
  # ##--males, faceted by case----
  # p1 = ggplot(mdfr1 %>% dplyr::filter(x=="male"),aes(x=z,y=val,colour=y)) +
  #        geom_line() + geom_point() +
  #        facet_wrap(~case,ncol=2) +
  #        labs(x="Size (mm CW)",y="selectivity",colour="year") +
  #        wtsPlots::getStdTheme(); if (testing) print(p1);
  # lbl = paste0("fshQuants.TCF.MaleSelFcns1.TCSAM02Mods");
  # cap = paste0("TCSAM02 models estimated selectivity curves for males in the directed fishery, ",
  #              "faceted by model scenario. ",
  #              "Curves labelled 1990 applies to all years before 1991. ",
  #              "Others apply in the year indicated in the legend.");
  # xt  = paste0("-TCF-SelFcnsM1");
  # lbl = wtsQMD::getLabel(xt);
  # pth = wtsQMD::getFigFN(xt);
  # lstFigs = c(lstFigs,wtsQMD::printGGplot(p1,lbl=lbl,cap=cap,pth=pth,ori="P"));

  ##--males, faceted by year----
  p1 = ggplot(mdfr1 %>% dplyr::filter(x=="male"),
              aes(x=z,y=val,colour=case,shape=case)) +
         geom_line() + geom_point() +
         facet_wrap(~y) +
         labs(x="Size (mm CW)",y="selectivity") +
         wtsPlots::getStdTheme(); if (testing) print(p1);
  lbl = paste0("fshQuants.TCF.MaleSelFcns2.TCSAM02Mods");
  cap = paste0("TCSAM02 models estimated selectivity curves for males in the directed fishery by year. ",
               "Curve labelled 1990 applies to  all years before 1991. ",
               "Others apply in the year indicated in the panel.");
  xt  = paste0("-TCF-SelFcnsM2");
  lbl = wtsQMD::getLabel(xt);
  pth = wtsQMD::getFigFN(xt);
  lstFigs = c(lstFigs,wtsQMD::printGGplot(p1,lbl=lbl,cap=cap,pth=pth,ori="P"));

  # ##--retention functions----
  # mdfr1 = rCompTCMs::extractMDFR.Fisheries.RetFcns(models[compare],
  #                                                  fleets=fleet_,
  #                                                  years=c(1990,1992,2005,2013),
  #                                                  cast="y+x") |> 
  #           dplyr::mutate(block=ifelse(y==1990,"before 1991","1991-1996"),
  #                         block=ifelse(y==2005,"2005-2009",block),
  #                         block=ifelse(y==2013,"2013-present",block),
  #                         block=factor(block,levels=c("before 1991","1991-1996","2005-2009","2013-present")));
  # p = ggplot(mdfr1,aes(x=z,y=val,colour=case)) +
  #       geom_line() + 
  #       geom_vline(xintercept=125,linetype=3) + 
  #       facet_wrap(~block,ncol=2) +
  #       ylim(0,1) +
  #       xlab('size (mm CW)')+ylab('retention')+
  #       wtsPlots::getStdTheme(); if (testing) print(p);
  # cap = paste0("TCSAM02 models estimated retention curves for males in the directed fishery by time block. ",
  #              "The dotted line indicates the current industry-preferred size (125 mm CW).");
  # xt  = paste0("-TCF-RetFcns");
  # lbl = wtsQMD::getLabel(xt);
  # pth = wtsQMD::getFigFN(xt);
  # lstFigs = c(lstFigs,wtsQMD::printGGplot(p,lbl=lbl,cap=cap,pth=pth,ori="P"));
  # rm(ps,p1,cap,xt,lbl,pth);
  # 
  # #--other fisheries----
  # ##--snow crab fishery----
  # fleet_="SCF";
  # ps = rCompTCMs::compareResults.Fisheries.Catchability(models[compare],
  #                                                       fleets=fleet_,
  #                                                       cast="x",
  #                                                       facet_grid=.~x,
  #                                                       years="all");
  # mdfr2 = rCompTCMs::extractMDFR.Fisheries.SelFcns(models[compare],
  #                                                       fleets=fleet_,
  #                                                       cast="y+x",
  #                                                       years=c(1990,2000,2020)) |> 
  #           dplyr::mutate(block=ifelse(y==1990,"before 1997","1997-2004"),
  #                         block=ifelse(y==2020,"2005-present",block));
  # p2 = ggplot(mdfr2,aes(x=z,y=val,colour=case)) + 
  #       geom_line() + 
  #       facet_grid(block~x) +
  #       labs(y="selectivity",x="size (mmCW)") +
  #       wtsPlots::getStdTheme() + noL;
  # pg = cowplot::plot_grid(ps[[1]]+ggL+noXT,p2,ncol=1,rel_heights=c(1,2)); if (testing) print(pg);
  # lbl = paste0("fshQuants.SCF.TCSAM02Mods");
  # cap = paste0("TCSAM02 models estimated fully-selected bycatch capture rates (not mortality) ",
  #              "and selectvity functions in the snow crab fishery. ",
  #              "Time blocks for selectivity functions are labelled: ",
  #              "1) before 1997; 2) 1997-2004; 3) 2005-present. ");
  # xt  = paste0("-SCF-CRs");
  # lbl = wtsQMD::getLabel(xt);
  # pth = wtsQMD::getFigFN(xt);
  # lstFigs = c(lstFigs,wtsQMD::printGGplot(pg,lbl=lbl,cap=cap,pth=pth,ori="P"));
  # rm(ps,mdfr2,p2,pg,lbl,cap,xt,lbl,pth);
  # 
  # ##--BBRKC fishery----
  # fleet_="RKF";
  # ps = rCompTCMs::compareResults.Fisheries.Catchability(models[compare],
  #                                                       fleets=fleet_,
  #                                                       cast="x",
  #                                                       facet_grid=.~x,
  #                                                       years="all");
  # mdfr2 = rCompTCMs::extractMDFR.Fisheries.SelFcns(models[compare],
  #                                                       fleets=fleet_,
  #                                                       cast="y+x",
  #                                                       years=c(1990,2000,2020)) |> 
  #           dplyr::mutate(block=ifelse(y==1990,"before 1997","1997-2004"),
  #                         block=ifelse(y==2020,"2005-present",block));
  # p2 = ggplot(mdfr2,aes(x=z,y=val,colour=case)) + 
  #       geom_line() + 
  #       facet_grid(block~x) +
  #       labs(y="selectivity",x="size (mmCW)") +
  #       wtsPlots::getStdTheme() + noL;
  # pg = cowplot::plot_grid(ps[[1]]+ggL+noXT,p2,ncol=1,rel_heights=c(1,2)); if (testing) print(pg);
  # lbl = paste0("fshQuants.RKF.TCSAM02Mods");
  # cap = paste0("TCSAM02 models estimated fully-selected bycatch capture rates (not mortality)  ",
  #              "and selectvity functions in the BBRKC fishery. ",
  #              "Time blocks for selectivity functions are: ",
  #              "1) before 1997; 2) 1997-2004; 3) 2005-present.");
  # xt  = paste0("-RKF-CRs");
  # lbl = wtsQMD::getLabel(xt);
  # pth = wtsQMD::getFigFN(xt);
  # lstFigs = c(lstFigs,wtsQMD::printGGplot(pg,lbl=lbl,cap=cap,pth=pth,ori="P"));
  # rm(ps,mdfr2,p2,pg,lbl,cap,xt,lbl,pth);
  # 
  # ##--groundfish fisheries----
  # fleet_="GF All";
  # ps = rCompTCMs::compareResults.Fisheries.Catchability(models[compare],
  #                                                       fleets=fleet_,
  #                                                       cast="x",
  #                                                       facet_grid=.~x,
  #                                                       years="all");
  # mdfr2 = rCompTCMs::extractMDFR.Fisheries.SelFcns(models[compare],
  #                                                       fleets=fleet_,
  #                                                       cast="y+x",
  #                                                       years=c(1980,1997,2020)) |> 
  #           dplyr::mutate(block=ifelse(y==1980,"before 1988","1987-1996"),
  #                         block=ifelse(y==2020,"1997-present",block));
  # p2 = ggplot(mdfr2,aes(x=z,y=val,colour=case)) + 
  #       geom_line() + 
  #       facet_grid(block~x) +
  #       labs(y="selectivity",x="size (mmCW)") +
  #       wtsPlots::getStdTheme() + noL;
  # pg = cowplot::plot_grid(ps[[1]]+ggL+noXT,p2,ncol=1,rel_heights=c(1,2)); if (testing) print(pg);
  # lbl = paste0("fshQuants.GFAll.TCSAM02Mods");
  # cap = paste0("TCSAM02 models estimated fully-selected bycatch capture rates (not mortality)  ",
  #              "and selectvity functions in the groundfish fisheries. ",
  #              "Time blocks for selectivity functions are: ",
  #              "1) before 1988; 2) 1987-1996; 3) 1997-present.");
  # xt  = paste0("-GFAll-CRs");
  # lbl = wtsQMD::getLabel(xt);
  # pth = wtsQMD::getFigFN(xt);
  # lstFigs = c(lstFigs,wtsQMD::printGGplot(pg,lbl=lbl,cap=cap,pth=pth,ori="P"));
  rm(ps,mdfr2,p2,pg,lbl,cap,xt,lbl,pth);
  rm(fleet_);
```


<!-- references -->
```{r,eval=!knitr::opts_knit$get("child")&!isPDF,results='asis'}
  cat("# References {-}\n");
  cat("::: {#refs}\n");
  cat(":::\n\n");
```

<!-- tables, if not child doc and lstTbls is not empty -->
```{r}
#| label: tables_TCSAM02Mods-FshQtys
#| eval: !expr '!knitr::opts_knit$get("child")'
#| results: asis
  source(system.file("files/printTablesSectionFromList.R",package="wtsQMD"));
```

<!-- figures, if not child doc and lstFigs is not empty -->
```{r}
#| label: figures_TCSAM02Mods-FshQtys
#| eval: !expr '!knitr::opts_knit$get("child")'
#| results: asis
  source(system.file("files/printFiguresSectionFromList.R",package="wtsQMD"));
```

