---
title: "Fits to Marginal Size Comps"
author: William T. Stockhausen
affiliation: NOAA/NMFS/AFSC
date: '`r format(Sys.time(), "%b %e, %Y")`'
fontsize: 11pt 
number-sections: true
reference-location: document
reference-section-title: References
bibliography: '`r path.expand("~/Work/Projects/Bibliography/AllRefs.bib")`'
csl: '`r system.file("files/CJFAS.csl",package="wtsQMD")`'
crossref:
  chapters: false      # prepend label reference numbers by chater number?
  fig-title: Figure    # for caption: default is "Figure")
  tbl-title: Table     # for caption: default is "Table")
  title-delim: "."     # for caption: default is ":")
  fig-prefix: Figure   # for in-text (use [-@fig-ref] to drop prefix in text)
  tbl-prefix: Table    # for in-text (use [-@tbl-ref] to drop prefix in text)
  fig-labels: arabic    # options are arabic, roman, roman i, alpha x, alpha X; latter two starting from x/X
  tbl-labels: arabic    # options are arabic, roman, roman i, alpha x, alpha X; latter two starting from x/X
  subref-labels: alpha a # options are arabic, roman, roman i, alpha x, alpha X; latter two starting from x/X
  ref-hyperlink: true    # references are hyperlinked if true
format: 
  html: 
    df-print: paged
    toc: true
    toc-location: right
    fig-width: 6.5
    fig-asp: 0.6
    fig-dpi: 100
  pdf:
    documentclass: scrartcl
    toc: false
    fig_crop: false
    keep-tex: false
    fig-width: 6.5
    fig-asp: 0.6
    fig-dpi: 100
    geometry:
      - left=1.0in
      - right=1.0in
      - top=1.0in
      - bottom=1.0in
      - textwidth=6.5in
      - showframe=false
    include-in-header: 
      - text: |
          \usepackage{placeins}
          \extrafloats{500}
          \maxdeadcycles=10000
          \usepackage{fontspec}
          \usepackage{multicol}
          \usepackage{hhline}
          \newlength\Oldarrayrulewidth
          \newlength\Oldtabcolsep
      - file: '`r system.file("files/ltx_ExtraLatexIncludes.tex",package="wtsQMD")`'
echo: false
warning: false
results: 'hide'
keep-md: false
keep-yaml: false
editor: source
editor_options: 
  chunk_output_type: console
concordance: true
params:
  setup: !expr 'system.file("files/qmd_setup.R",package="wtsQMD")'
  testing: false
---

<!-- if not child doc, set up required objects -->
```{r}
#| label: TCSAM02Mods-MrgZCs_setup
#| eval: !expr '!knitr::opts_knit$get("child")'
#| results: "asis"
  if (!exists("testing")) testing = params$testing;
  if (testing) cat(params$setup,"\n\n")
  source(params$setup);
  if (testing) {
    cat("In MargZCsPrefMod_setup:\n\n")
    cat("root = ",root,"\n\n");
    cat("peek = '",child_path$peek(),"'\n\n",sep="");
  }
```

```{r}
#| label: setup_TCSAM02Mods-MrgZCs
#| results: 'asis'
  require(ggplot2);
  require(kableExtra);
  require(tables);
  require(wtsQMD);
  Sum = wtsUtilities::Sum;
  old_thm = ggplot2::theme_set(cowplot::theme_cowplot(font_size = 10) +
                               cowplot::background_grid() +
                               cowplot::panel_border());
  thm = wtsPlots::getStdTheme();
  options("readr.show_col_types"=FALSE);
  if (testing) cat("dirThs =",child_path$peek(),"\n\n")
  # if (!exists("s")){
  #   fn = ifelse(child_path$peek()!="",
  #               file.path(child_path$peek(),"../../",params$rdaAsmtSetup),
  #               file.path(rstudioapi::getActiveProject(),params$rdaAsmtSetup));
  #   s = wtsUtilities::getObj(fn);
  # }
  # if (!exists("models"))
  #   models = wtsUtilities::getObj(s$ModCompPths$fnModels);
  dirThs = child_path$peek();                #--path to "this" folder
  dirPrj = file.path(child_path$peek(),"..");#--path to project folder from "this" folder
  if (!exists("models"))
    models = wtsUtilities::getObj(file.path(dirThs,"rda_Models.RData"));

  if (!exists("asmtYr")) asmtYr = 2024;

  if (!exists("strAY"))  strAY  = wtsQMD::crabYear(asmtYr);
  if (!exists("currYr")) currYr = wtsQMD::crabYear(asmtYr-1);#--current fishery year

  prvYr = asmtYr-1;
  if (!exists("tblno")) tblno = 0;#--index in LETTERS for tables in text
```

```{r}
  prvMod = "22.03d5";#--previous assessment model
  compare  = names(models);
  cases1   = compare;
  cases2   = NULL;
  obs_case = prvMod;
   if (!exists("PLOT_OBJECTS")){
    #--PLOT OBJECTS---------------------------------------
    source(file.path(dirThs,"../RCode_Markdown/r_FigureFunctions.R"));
    std_theme = wtsPlots::getStdTheme();
    ggT = ggplot2::theme(plot.title=element_text(size=10,margin=margin()),
                         panel.spacing = grid::unit(0.01,"in"),
                         legend.position="none", 
                         plot.margin=margin(0,0,0,1));
    ggL = labs(title=NULL,subtitle=NULL);
    colour_scale=ggplot2::scale_color_hue();
    fill_scale  =ggplot2::scale_fill_hue();
    PLOT_OBJECTS = "PLOT_OBJECTS";#--make flag to prevent doing this again
  }
  ggT1 = ggplot2::theme(plot.title=element_text(size=10,margin=margin()),
                       panel.spacing = grid::unit(0.01,"in"),
                       plot.margin=margin(0,0,0,1));
```

## Marginal Distributions for Fits to Compositional Data {#sec-TCSAM02Mods-MrgZCs}

Marginal distributions for fits to the compositional data from the fisheries are shown in 
Figures [-@fig-TCSAM02Mods-MrgZCs-TCF]-[-@fig-TCSAM02Mods-MrgZCs-GFAll]. Marginal distributions for fits to the compositional data from the surveys are shown in Figure [-@fig-TCSAM02Mods-MrgZCs-Surveys]. Except for the BSFRF survey data, the fits to the marginal distributions are practically identical across all the models and none exhibit the problem with overpredicting the proportions of large crab noted for the fits to individual years because underpredictions in the early parts of the time series balance out overpredictions in the latter part of those time series. The models do exhibit some variability with respect to the marginal distributions for the BSFRF size compositions, reflecting the differences in fit to the individual size compositions and the relatively few years to available to form the marginal distributions.

```{r}
#| label: fig-TCSAM02Mods-MrgZCs-TCF
#| fig-width: 9
#| fig-asp: 0.667
  #----fisheries
  #------directed fishery
  #--------retained catch
selCases = cases1;
  mdfr<-rCompTCMs::extractFits.MeanSizeComps(objs=models[selCases],
                                              fleets="TCF",
                                              fleet.type="fishery",
                                              catch.type="retained",
                                              years="all",
                                              plot1stObs=FALSE) |> 
          dplyr::filter(!((type=="observed")&(!(case %in% c("22.03d5","25_01")))));
  ps = rCompTCMs::compareFits.MeanSizeComps(mdfr=mdfr,fleets="TCF",
                                            fleet.type="fishery",catch.type="retained",
                                            plot1stObs=FALSE)[1];
  lg = cowplot::get_legend(ps[[1]]+guides(shape="none")+theme(legend.box.margin=margin(0,0,0,2)));
  p1 = ps[[1]]+ggL+ggT+theme(axis.title.x = element_blank());
  #--total catch for model scenarios
  mdfr<-rCompTCMs::extractFits.MeanSizeComps(objs=models[selCases],
                                              fleets="TCF",
                                              fleet.type="fishery",
                                              catch.type="total",
                                              years="all",
                                              plot1stObs=FALSE) |> 
          dplyr::filter(!((type=="observed")&(!(case %in% c("22.03d5","25_01")))));
  ps = rCompTCMs::compareFits.MeanSizeComps(mdfr=mdfr,fleets="TCF",
                                            fleet.type="fishery",catch.type="total",
                                            plot1stObs=FALSE)[1];
  p2 = ps[[1]]+ggL+ggT+theme(axis.title.x = element_blank());
  pg1 = cowplot::plot_grid(p1+std_theme,p2+std_theme,ncol=1,rel_heights=c(1,1));
  pg2 = cowplot::plot_grid(pg1,lg,nrow=1,rel_widths = c(10,1.5));
  cap = paste0("TCSAM02 models fits to directed fishery mean size compositions. Upper plot: retained catch; ",
               "lower plot: total catch. ",
               "22.03d5 is the model from the previous assessment and had tail compression applied.");
  lbl = wtsQMD::getLabel();
  pth = wtsQMD::getFigFN();
  lstFigs = c(lstFigs,wtsQMD::printGGplot(pg2,lbl=lbl,cap=cap,pth=pth,ori="L"));
```  

```{r}
#| label: fig-TCSAM02Mods-MrgZCs-SCF
#| fig-width: 9
#| fig-asp: 0.667
  #------SCF
  #--------total catch for model scenarios
  mdfr<-rCompTCMs::extractFits.MeanSizeComps(objs=models[selCases],
                                              fleets="SCF",
                                              fleet.type="fishery",
                                              catch.type="total",
                                              years="all",
                                              plot1stObs=FALSE) |> 
          dplyr::filter(!((type=="observed")&(!(case %in% c("22.03d5","25_01")))));
  ps = rCompTCMs::compareFits.MeanSizeComps(mdfr=mdfr,fleets="SCF",
                                            fleet.type="fishery",catch.type="total",
                                            plot1stObs=FALSE)[1];
  p2 = ps[[1]]+ggL+ggT1;
  cap = paste0("TCSAM02 models fits to mean bycatch size compositions from the snow crab fishery. ",
               "22.03d5 is the model from the previous assessment and had tail compression applied.");
  lbl = wtsQMD::getLabel();
  pth = wtsQMD::getFigFN();
  lstFigs = c(lstFigs,wtsQMD::printGGplot(p2,lbl=lbl,cap=cap,pth=pth,ori="L"));
```

```{r}
#| label: fig-TCSAM02Mods-MrgZCs-RKF
#| fig-width: 9
#| fig-asp: 0.667
  #--------RKF
  mdfr<-rCompTCMs::extractFits.MeanSizeComps(objs=models[selCases],
                                              fleets="RKF",
                                              fleet.type="fishery",
                                              catch.type="total",
                                              years="all",
                                              plot1stObs=FALSE) |> 
          dplyr::filter(!((type=="observed")&(!(case %in% c("22.03d5","25_01")))));
  ps = rCompTCMs::compareFits.MeanSizeComps(mdfr=mdfr,fleets="RKF",
                                            fleet.type="fishery",catch.type="total",
                                            plot1stObs=FALSE)[1];
  p2 = ps[[1]]+ggL+ggT1;
  cap = paste0("TCSAM02 models fits to mean bycatch size compositions from the BBRKC fishery. ",
               "22.03d5 is the model from the previous assessment and had tail compression applied.");
  lbl = wtsQMD::getLabel();
  pth = wtsQMD::getFigFN();
  lstFigs = c(lstFigs,wtsQMD::printGGplot(p2,lbl=lbl,cap=cap,pth=pth,ori="L"));
```
```{r}
#| label: fig-TCSAM02Mods-MrgZCs-GFAll
#| fig-width: 9
#| fig-asp: 0.667
  #--------GF
  #--------total catch for ALL model scenarios
  mdfr<-rCompTCMs::extractFits.MeanSizeComps(objs=models[selCases],
                                              fleets="GF All",
                                              fleet.type="fishery",
                                              catch.type="total",
                                              years="all",
                                              plot1stObs=FALSE) |> 
          dplyr::filter(!((type=="observed")&(!(case %in% c("22.03d5","25_01")))));
  ps = rCompTCMs::compareFits.MeanSizeComps(mdfr=mdfr,fleets="GF All",
                                            fleet.type="fishery",catch.type="total",
                                            plot1stObs=FALSE)[1];
  p2 = ps[[1]]+ggL+ggT1;
  cap = paste0("TCSAM02 models fits to mean bycatch size compositions from the groundfish fisheries. ",
               "The total catch size compositions were normalized similarly for all model scenarios. ",
               "22.03d5 is the model from the previous assessment and had tail compression applied.");
  lbl = wtsQMD::getLabel();
  pth = wtsQMD::getFigFN();
  lstFigs = c(lstFigs,wtsQMD::printGGplot(p2,lbl=lbl,cap=cap,pth=pth,ori="L"));
```

```{r}
#| label: fig-TCSAM02Mods-MrgZCs-Surveys
#| fig-width: 9
#| fig-asp: 0.667
  #--surveys----
  ##--NMFS----
  mdfr<-rCompTCMs::extractFits.MeanSizeComps(objs=models[selCases],
                                              fleets="NMFS M",fleet.type="survey",
                                              catch.type="index",years="all",
                                              plot1stObs=FALSE) |> 
          dplyr::filter(!((type=="observed")&(!(case %in% c("22.03d5","25_01")))));
  ps = rCompTCMs::compareFits.MeanSizeComps(mdfr=mdfr,fleets="NMFS M",
                                            fleet.type="survey",catch.type="index",
                                            plot1stObs=FALSE)[1];
  lg = cowplot::get_legend(ps[[1]]+guides(shape="none")+theme(legend.box.margin=margin(0,0,0,2)));
  p1 = ps[[1]]+ggL+ggT+theme(axis.title.x = element_blank())+labs(title="NMFS");
  mdfr<-rCompTCMs::extractFits.MeanSizeComps(objs=models[selCases],
                                              fleets="NMFS F",fleet.type="survey",
                                              catch.type="index",years="all",
                                              plot1stObs=FALSE) |> 
          dplyr::filter(!((type=="observed")&(!(case %in% c("22.03d5","25_01")))));
  ps = rCompTCMs::compareFits.MeanSizeComps(mdfr=mdfr,fleets="NMFS F",
                                         fleet.type="survey",catch.type="index",
                                         plot1stObs=FALSE)[1];
  p2 = ps[[1]]+ggL+ggT+theme(axis.title.x = element_blank())+labs(title=" ");
  pg1 = cowplot::plot_grid(p1 + std_theme,p2 + std_theme,ncol=1,rel_heights=c(2,3))
  ##--BSFRF----
  mdfr<-rCompTCMs::extractFits.MeanSizeComps(objs=models[selCases],
                                              fleets="SBS BSFRF M",fleet.type="survey",
                                              catch.type="index",years="all",
                                              plot1stObs=FALSE) |> 
          dplyr::filter(!((type=="observed")&(!(case %in% c("22.03d5","25_01")))));
  ps = rCompTCMs::compareFits.MeanSizeComps(mdfr=mdfr,fleets="SBS BSFRF M",
                                         fleet.type="survey",catch.type="index",
                                         plot1stObs=FALSE)[1];
  p3 = ps[[1]]+ggL+ggT+theme(axis.title.x = element_blank(),axis.title.y=element_blank())+labs(title="BSFRF");
  mdfr<-rCompTCMs::extractFits.MeanSizeComps(objs=models[selCases],
                                              fleets="SBS BSFRF F",fleet.type="survey",
                                              catch.type="index",years="all",
                                              plot1stObs=FALSE) |> 
          dplyr::filter(!((type=="observed")&(!(case %in% c("22.03d5","25_01")))));
  ps = rCompTCMs::compareFits.MeanSizeComps(models[selCases],fleets="SBS BSFRF F",
                                         fleet.type="survey",catch.type="index",
                                         plot1stObs=FALSE)[1];
  p4 = ps[[1]]+ggL+ggT+theme(axis.title.x=element_blank(),axis.title.y=element_blank())+labs(title=" ");
  pg2 = cowplot::plot_grid(p3 + std_theme,p4 + std_theme,ncol=1,rel_heights = c(2,3));
  ##--combine plots as columns----
  pg3 = cowplot::plot_grid(pg1,pg2,lg,nrow=1,rel_widths = c(10,10,2)); if (testing) print(pg3);
  cap = paste0("TCSAM02 models' fits to mean survey size compositions from the NMFS EBS (left column) ",
               "and BSFRF SBS (right column) surveys. ",
               "22.03d5 is the model from the previous assessment and had tail compression applied.",
               "The total catch size compositions were normalized similarly for all model scenarios. ");
  lbl = wtsQMD::getLabel();
  pth = wtsQMD::getFigFN();
  lstFigs = c(lstFigs,wtsQMD::printGGplot(pg3,lbl=lbl,cap=cap,pth=pth,ori="L"));
```

<!-- references -->
```{r,eval=!knitr::opts_knit$get("child")&!isPDF,results='asis'}
  cat("# References {-}\n");
  cat("::: {#refs}\n");
  cat(":::\n\n");
```

<!-- tables, if not child doc and lstTbls is not empty -->
```{r}
#| label: tables_TCSAM02Mods-MrgZCs
#| eval: !expr '!knitr::opts_knit$get("child")'
#| results: asis
  source(system.file("files/printTablesSectionFromList.R",package="wtsQMD"));
```

<!-- figures, if not child doc and lstFigs is not empty -->
```{r}
#| label: figures_TCSAM02Mods-MrgZCs
#| eval: !expr '!knitr::opts_knit$get("child")'
#| results: asis
  source(system.file("files/printFiguresSectionFromList.R",package="wtsQMD"));
```

