---
title: "Success or failure of small Tanner crab"
author: "William T. Stockhausen"
institute: NOAA/NMFS/AFSC
date: '`r format(Sys.time(), "%b %e, %Y")`'
fontsize: 11pt 
number-sections: true
reference-location: document
bibliography: '`r path.expand("~/Work/Projects/Bibliography/AllRefs.bib")`'
csl: '`r system.file("files/CJFAS.csl",package="wtsQMD")`'
link-citations: true
crossref:
  chapters: false      # prepend label reference numbers by chater number?
  fig-title: Figure    # for caption: default is "Figure")
  tbl-title: Table     # for caption: default is "Table")
  title-delim: "."     # for caption: default is ":")
  fig-prefix: Figure   # for in-text (use [-@fig-ref] to drop prefix in text)
  tbl-prefix: Table    # for in-text (use [-@tbl-ref] to drop prefix in text)
  fig-labels: arabic    # options are arabic, roman, roman i, alpha x, alpha X; latter two starting from x/X
  tbl-labels: arabic    # options are arabic, roman, roman i, alpha x, alpha X; latter two starting from x/X
  subref-labels: alpha a # options are arabic, roman, roman i, alpha x, alpha X; latter two starting from x/X
  ref-hyperlink: true    # references are hyperlinked if true
format: 
  html: 
    df-print: paged
    toc: true
    toc-location: right
    fig-width: 8
    fig-asp: 1.4
    fig-dpi: 100
    embed-resources: true
    include-in-header: 
      - '`r system.file("files/in-line_math_mode.html",package="wtsQMD")`'
  pdf:
    documentclass: scrartcl
    toc: false
    fig_crop: false
    keep-tex: false
    geometry:
      - left=1.0in
      - right=1.0in
      - top=1.0in
      - bottom=1.0in
      - textwidth=6.5in
      - showframe=false
    include-in-header: 
      - text: |
          \usepackage{placeins}
          \extrafloats{500}
          \maxdeadcycles=10000
          \usepackage{fontspec}
          \usepackage{multicol}
          \usepackage{hhline}
          \newlength\Oldarrayrulewidth
          \newlength\Oldtabcolsep
      - file: '`r system.file("files/ltx_ExtraLatexIncludes.tex",package="wtsQMD")`'
echo: false
warning: false
results: 'hide'
keep-md: false
keep-yaml: false
editor: source
editor_options: 
  chunk_output_type: console
concordance: true
params:
  setup: !expr 'system.file("files/qmd_setup.R",package="wtsQMD")'
  dirAsmt: "~/Work/StockAssessments-Crab/Assessments/TannerCrab/2024-09_TannerCrab/AssessmentData/Data_Surveys_NMFS"
  testing: false
---
<!-- IMPORTANT: if used as a child doc, all chunk labels must be unique within the overall document -->

<!-- 
  NOTEs: 
     * child_path$peek() gives path to current script folder.
     * before starting a child document, do 
         "child_path$push(file.path(child_path$peek(),rel_path))" first, 
         where rel_path is the relative path to the child
     * after a child document has finished, do "child_path$pop()" to return to current path value
-->

<!-- if not child doc, set up required objects -->
```{r}
#| label: SmallCrabSuccess_setup
#| eval: !expr '!knitr::opts_knit$get("child")'
#| results: "asis"
  testing = params$testing;
  if (testing) cat(params$setup,"\n\n")
  source(params$setup);
  if (testing) cat("root = ",root,"\n\n")
```

```{r}
#| label: setup_SCsxs
#| results: 'asis'
  require(crabpack);
  require(ggplot2);
  require(kableExtra);
  require(tables);
  
  #--path to folder containing "this" file
  dirThs = child_path$peek();
  if (rstudioapi::isAvailable()) dirThs = dirname(rstudioapi::getActiveDocumentContext()$path);

  #--constants
  MILLION  = 1000000;
  THOUSAND = 1000;
```

```{r SCsxs_getList}
  lst = wtsUtilities::getObj(file.path(dirThs,"rda_SmallCrabSuccess.RData"))
```

## Small crab success {#sec-SCsxs}

Small Tanner crab encountered during the NMFS EBS bottom trawl surveys in 2003-2005 and 2008-2010 successfully propagated to larger sizes while the cohort first observed in 2017-2019 did not (Figure [-@fig-SCsxs-ZCs]). The SSC requested that the author explore whether the "successful" cohorts showed differences in habitat use compared with the "unsuccessful" one that may have contributed to their success. Furthermore, the SSC recommended that a comparison of environmental conditions experienced by small crabs during these periods may help to elucidate why some cohorts appear to propagate and others do not. Below, I present some simple comparisons between the cohorts using NMFS EBS bottom trawl survey data with regards to the bottom temperatures experienced by small crab (Figures [-@fig-SCsxs-SCAvT] and [-@fig-SCsxs-TvSCA]), overlap with large crab (Figures [-@fig-SCsxs-SCAvLCA] and [-@fig-SCsxs-LCAvSCA]), the distribution of small crab with respect to the joint distribution of bottom temperature and large crab abundance (Figures [-@fig-SCsxs-H2Ds1]-[-@fig-SCsxs-H2Ds3]), and finally the geographic distributions of the cohorts with respect to location on the EBS shelf and relation to the cold pool (i.e., bottom temperature < 2^o^C; Figure [-@fig-SCsxs-Maps]). Bottom temperature was chosen because it is important for physiological processes and regulating feeding, respiration, and growth. Large crab CPUE was chosen because of the possibility that predation by, or competition with, large crab might have a substantial effect on small crab survival. Both were co-extensive with small crab abundance in the survey data.

The small crab in all three cohorts were exposed to a range of bottom temperatures from ~-2 to ~6^o^C. Survey CPUE peaked in the 4 to 6^o^C range for all three cohorts (Figure [-@fig-SCsxs-SCAvT]), but crab in the "successful" cohorts experienced lower mean temperatures across the range of crab densities (Figure [-@fig-SCsxs-TvSCA]) when compared with the 2017-2019 "unsuccessful" cohort.

There seemed to be little difference between the cohorts in terms of the densities of large crab experienced by small crab, or the densities of small crab associated with large crab (Figures [-@fig-SCsxs-SCAvLCA] and [-@fig-SCsxs-LCAvSCA]). The  "successful" cohorts appeared to occupy a wider range of temperature and large crab densities than the "unsuccessful" cohort, in which most crab were associated with warm temperatures and low large crab densities (Figures [-@fig-SCsxs-H2Ds1]-[-@fig-SCsxs-H2Ds3]). The location and size of the cold pool varied annually in relation to spatial extent of the three cohorts, with no clear pattern apparent (Figure [-@fig-SCsxs-Maps]). It was small and located to the northwest during 2003-05, extensive during 2008-10, and started out extensive but then essentially disappeared after the first year in 2017-2019.

The one clear difference between the "successful" cohorts and the "unsuccessful" cohort is mean bottom temperature, with the "successful" cohorts experiencing colder temperatures relative to those experienced by the "unsuccessful" cohort. A more nuanced analysis might pull out more subtle relationships, but any further analysis faces the issue of small sample size (only three cohorts) and the potential for identifying spurious relationships. Expanding the time frame considered to the entire period covered by the NMF survey might increase the sample size by a factor of three or four successful/unsuccessful cohorts over the 50 year extent of the survey. Further work needs to be done in coordination with SAP and perhaps be led by analysts developing the Tanner crab Ecosystem and Socioeconomic Profile (ESP).

```{r}
#| label: fig_SCsxs-ZCs
#| results: asis
#| fig-width: 6.5 
#| fig-asp: 1.2
  dfrZCs = lst$dfrZCs;
  p = wtsSizeComps::plotSizeCompsAsRidges(
        dfrZCs |> dplyr::filter(!is.na(cohort)) |> dplyr::mutate(group=cohort),
        sizes_in="z",
        values_in="totAbd",
        y_positions="year",
        group_by=c("cohort","year"),
        xlim=c(25,150),
        ylim=c(2004,2022),
        colour="cohort",
        fill="cohort");
  lbl = wtsQMD::getLabel();
  cap = paste0("Progression of Tanner crab size compositions for successful (2003-2005; 2008-2010) and  ",
               "unsuccessful (2017-2021) pseudocohorts from the NMFS EBS bottom trawl survey across five years.")
  pth = wtsQMD::getFigFN();
  lstFigs = c(lstFigs,wtsQMD::printGGplot(p,lbl=lbl,cap=cap,pth=pth,ori="P"));
  rm(p,lbl,cap,pth,dfrZCs);
```

```{r}
#| label: fig_SCsxs-SCAvT
#| results: asis
#| fig-width: 6.5 
#| fig-asp: 1.0
  dfrSTC = lst$dfrSTC;
  p = ggplot(dfrSTC |> dplyr::filter(!is.na(cohort),numCPUE_STC>0),aes(x=temp,y=numCPUE_STC,colour=cohort)) +
        geom_point(alpha=0.5) +
        geom_smooth() + 
        scale_y_log10() +
        labs(x="temperature degC",y="small crab CPUE (number/sq. nmi.)") +
        wtsPlots::getStdTheme() +
        theme(legend.position="inside",
              legend.position.inside=c(0.01,0.99),
              legend.justification.inside=c(0,1));
  lbl = wtsQMD::getLabel();
  cap = paste0("Small crab haul-specific CPUE plotted against bottom temperature for the ",
               "successful 2003-2005 and 2008-2010 pseudocohorts and the unsuccessful 2017-2019 one. ",
               "Lines and shading represent smooth fits to the ln-scale CPUE data as a function of temperature.")
  pth = wtsQMD::getFigFN();
  lstFigs = c(lstFigs,wtsQMD::printGGplot(p,lbl=lbl,cap=cap,pth=pth,ori="P"));
  rm(p,lbl,cap,pth);
```

```{r}
#| label: fig_SCsxs-TvSCA
#| results: asis
#| fig-width: 6.5 
#| fig-asp: 1.0
  p = ggplot(dfrSTC |> dplyr::filter(!is.na(cohort),numCPUE_STC>0),aes(y=temp,x=numCPUE_STC,colour=cohort)) +
        geom_point(alpha=0.5) +
        geom_smooth() + 
        scale_x_log10() +
        labs(y="temperature degC",x="small crab CPUE (number/sq. nmi.)") +
        wtsPlots::getStdTheme() +
        theme(legend.position="inside",
              legend.position.inside=c(0.01,0.99),
              legend.justification.inside=c(0,1));
  lbl = wtsQMD::getLabel();
  cap = paste0("Bottom temperature plotted against small crab haul-specific CPUE for the ",
               "successful 2003-2005 and 2008-2010 pseudocohorts and the unsuccessful 2017-2019 one. ",
               "Lines and shading represent smooth fits to the temperature data as a function of ln-scale CPUE.")
  pth = wtsQMD::getFigFN();
  lstFigs = c(lstFigs,wtsQMD::printGGplot(p,lbl=lbl,cap=cap,pth=pth,ori="P"));
  rm(p,lbl,cap,pth);
```

```{r}
#| label: fig_SCsxs-SCAvLCA
#| results: asis
#| fig-width: 6.5 
#| fig-asp: 1.0
  p = ggplot(dfrSTC |> dplyr::filter(!is.na(cohort),numCPUE_STC>0),aes(x=numCPUE_LTC,y=numCPUE_STC,colour=cohort)) +
        geom_point(alpha=0.5) + 
        geom_smooth() + 
        scale_y_log10() +
        scale_x_log10(limits=c(NA,10000)) +
        labs(x="large crab CPUE (number/sq. nmi.)",y="small crab CPUE (number/sq. nmi.)") +
        wtsPlots::getStdTheme() +
        theme(legend.position="inside",
              legend.position.inside=c(0.01,0.99),
              legend.justification.inside=c(0,1));
  lbl = wtsQMD::getLabel();
  cap = paste0("Small crab haul-specific CPUE plotted against large crab haul-specific CPUE for the ",
               "successful 2003-2005 and 2008-2010 pseudocohorts and the unsuccessful 2017-2019 one. ",
               "Lines and shading represent smooth fits to the small crab CPUE data as a function of ",
               "the large crab CPUE data.")
  pth = wtsQMD::getFigFN();
  lstFigs = c(lstFigs,wtsQMD::printGGplot(p,lbl=lbl,cap=cap,pth=pth,ori="P"));
  rm(p,lbl,cap,pth);
```

```{r}
#| label: fig_SCsxs-LCAvSCA
#| results: asis
#| fig-width: 6.5 
#| fig-asp: 1.0
  p = ggplot(dfrSTC |> dplyr::filter(!is.na(cohort),numCPUE_STC>0),aes(y=numCPUE_LTC,x=numCPUE_STC,colour=cohort)) +
        geom_point(alpha=0.5) + 
        geom_smooth() + 
        scale_x_log10() +
        scale_y_log10(limits=c(NA,10000)) +
        labs(y="large crab CPUE (number/sq. nmi.)",x="small crab CPUE (number/sq. nmi.)") +
        wtsPlots::getStdTheme() +
        theme(legend.position="inside",
              legend.position.inside=c(0.01,0.99),
              legend.justification.inside=c(0,1));
  lbl = wtsQMD::getLabel();
  cap = paste0("Large crab haul-specific CPUE plotted against small crab haul-specific CPUE for the ",
               "successful 2003-2005 and 2008-2010 pseudocohorts and the unsuccessful 2017-2019 one. ",
               "Lines and shading represent smooth fits to the ln-scale large crab CPUE data as a function of ",
               "the ln-scale small crab CPUE data.")
  pth = wtsQMD::getFigFN();
  lstFigs = c(lstFigs,wtsQMD::printGGplot(p,lbl=lbl,cap=cap,pth=pth,ori="P"));
  rm(p,lbl,cap,pth);
```

```{r}
#| label: fig_SCsxs-H2Ds1
#| results: asis
#| fig-width: 6.5 
#| fig-asp: 1.0
  p = wtsPlots::ggMarginal_Hist2D(dfrSTC |> dplyr::filter(year %in% 2003:2005),
                                  x=numCPUE_LTC,y=temp,weight=numCPUE_STC,
                                  xparams=list(limits=c(0,10000)),
                                  yparams=list(limits=c(-2,10)),
                                  addValues=FALSE,
                                  xlab="large crab CPUE (number/sq. nmi.)",
                                  ylab="temp. (deg C)",
                                 );
  lbl = wtsQMD::getLabel();
  cap = paste0("Relative abundance of small crab as a function of large crab CPUE and temperature for the ",
               "successful 2003-2005 pseudocohort.")
  pth = wtsQMD::getFigFN();
  lstFigs = c(lstFigs,wtsQMD::printGGplot(p,lbl=lbl,cap=cap,pth=pth,ori="P"));
  rm(p,lbl,cap,pth);
```

```{r}
#| label: fig_SCsxs-H2Ds2
#| results: asis
#| fig-width: 6.5 
#| fig-asp: 1.0
  p = wtsPlots::ggMarginal_Hist2D(dfrSTC |> dplyr::filter(year %in% 2008:2010),
                                  x=numCPUE_LTC,y=temp,weight=numCPUE_STC,
                                  xparams=list(limits=c(0,10000)),
                                  yparams=list(limits=c(-2,10)),
                                  addValues=FALSE,
                                  xlab="large crab CPUE (number/sq. nmi.)",
                                  ylab="temp. (deg C)",
                                 );
  lbl = wtsQMD::getLabel();
  cap = paste0("Relative abundance of small crab as a function of large crab CPUE and temperature for the ",
               "successful 2008-2010 pseudocohort.")
  pth = wtsQMD::getFigFN();
  lstFigs = c(lstFigs,wtsQMD::printGGplot(p,lbl=lbl,cap=cap,pth=pth,ori="P"));
  rm(p,lbl,cap,pth);
```

```{r}
#| label: fig_SCsxs-H2Ds3
#| results: asis
#| fig-width: 6.5 
#| fig-asp: 1.0
  p = wtsPlots::ggMarginal_Hist2D(dfrSTC |> dplyr::filter(year %in% 2017:2019),
                                  x=numCPUE_LTC,y=temp,weight=numCPUE_STC,
                                  xparams=list(limits=c(0,10000)),
                                  yparams=list(limits=c(-2,10)),
                                  addValues=FALSE,
                                  xlab="large crab CPUE (number/sq. nmi.)",
                                  ylab="temp. (deg C)",
                                 );
  lbl = wtsQMD::getLabel();
  cap = paste0("Relative abundance of small crab as a function of large crab CPUE and temperature for the ",
               "unsuccessful 2017-2019 pseudocohort.")
  pth = wtsQMD::getFigFN();
  lstFigs = c(lstFigs,wtsQMD::printGGplot(p,lbl=lbl,cap=cap,pth=pth,ori="P"));
  rm(p,lbl,cap,pth);
```

```{r}
#| label: fig_SCsxs-Maps
#| results: asis
#| fig-width: 6.5 
#| fig-asp: 1.0
  years = c(2003:2005,2008:2010,2017:2019);
  sfSTC = dfrSTC |>
            dplyr::group_by(year) |>
            dplyr::mutate(nrmCPUE_STC=numCPUE_STC/sum(numCPUE_STC),
                          nrmCPUE_LTC=numCPUE_LTC/sum(numCPUE_LTC)) |>
            dplyr::left_join(lst$smos$lstSrvGrids$grid,by=c("GIS_STATION"="STATION_ID")) |>
            sf::st_as_sf();
  p = ggplot() + lst$bmls$land + lst$bmls$bathym +
         geom_sf(data=sfSTC |> dplyr::filter(year %in% years,nrmCPUE_STC>0),
                          mapping=aes(colour=nrmCPUE_STC,fill=nrmCPUE_STC)) +
         geom_sf(data=lst$smos$sfCP |> dplyr::filter(year %in% years),
                           colour="black",fill=NA,linewidth=1) +
         scale_fill_viridis_c(name="small crab CPUE\n(normalized)",option="plasma",
                              limits=c(0,NA),oob=scales::squish,direction=-1,
                              aesthetics=c("colour","fill")) +
         facet_wrap(~year,ncol=3,scales="fixed") +
         lst$bmls$map_scale + lst$bmls$theme +
         theme(legend.position="top",
               #legend.position.inside=c(0.01,0.01),
               legend.justification.top=c(0,0),
               legend.direction="horizontal");
  lbl = wtsQMD::getLabel();
  cap = paste0("Relative abundance of small crab (color scale) at NMF EBS bottom trawl survey stations for the  ",
               "two successful (2003-2005, 2008-2010) and one unsuccessful (2017-2019) psuedocohort. The annual ",
               "extent of 2 deg C or colder 'cold pool' water (as determined by bottom temperature at the survey stations) is ",
               "indicated by the black outline.")
  pth = wtsQMD::getFigFN();
  lstFigs = c(lstFigs,wtsQMD::printGGplot(p,lbl=lbl,cap=cap,pth=pth,ori="P"));
  rm(p,lbl,cap,pth,dfrSTC,sfSTC,lst);
```

<!-- references, if not child doc -->
```{r,eval=!knitr::opts_knit$get("child")&!isPDF,results='asis'}
  cat("# References {-}\n");
  cat("::: {#refs}\n");
  cat(":::\n\n");
```

<!-- tables, if not child doc and lstTbls is not empty -->
```{r}
#| label: tables_SCsxs
#| eval: !expr '!knitr::opts_knit$get("child")'
#| results: asis
  source(system.file("files/printTablesSectionFromList.R",package="wtsQMD"));
```

<!-- figures, if not child doc and lstFigs is not empty -->
```{r}
#| label: figures_SCsxs
#| eval: !expr '!knitr::opts_knit$get("child")'
#| results: asis
  source(system.file("files/printFiguresSectionFromList.R",package="wtsQMD"));
```
