---
title: "2025 Tanner Crab Assessment Considerations"
author:
- name: William T. Stockhausen
  affiliations:
    - id: afsc-refm
      name: "Alaska Fisheries Science Center"
      department: "Resource Ecology and Fisheries Management"
      address: 
        - "7600 Sand Point Way N.E."
        - "Seattle, Washington 98115-6349"
date: '`r format(Sys.time(), "%b %e, %Y")`'
fontsize: 11pt 
number-sections: true
number-depth: 3
reference-location: document
reference-section-title: References
bibliography: '`r path.expand("~/Work/Projects/Bibliography/AllRefs.bib")`'
csl: '`r system.file("files/CJFAS.csl",package="wtsQMD")`'
link-citations: true
crossref:
  chapters: false      # prepend label reference numbers by chater number?
  fig-title: Figure    # for caption: default is "Figure")
  tbl-title: Table     # for caption: default is "Table")
  title-delim: "."     # for caption: default is ":")
  fig-prefix: Figure   # for in-text (use [-@fig-ref] to drop prefix in text)
  tbl-prefix: Table    # for in-text (use [-@tbl-ref] to drop prefix in text)
  fig-labels: arabic    # options are arabic, roman, roman i, alpha x, alpha X; latter two starting from x/X
  tbl-labels: arabic    # options are arabic, roman, roman i, alpha x, alpha X; latter two starting from x/X
  subref-labels: alpha a # options are arabic, roman, roman i, alpha x, alpha X; latter two starting from x/X
  ref-hyperlink: true    # references are hyperlinked if true
format: 
  html: 
    df-print: paged
    toc: true
    toc-location: right
    fig-width: 8
    fig-asp: 0.4
    fig-dpi: 100
    embed-resources: true
    include-in-header: 
      - '`r system.file("files/in-line_math_mode.html",package="wtsQMD")`'
  pdf:
    documentclass: scrartcl
    toc: false
    fig_crop: false
    keep-tex: false
    fig-width: 6.5
    fig-asp: 0.4
    geometry:
      - left=1.0in
      - right=1.0in
      - top=1.0in
      - bottom=1.0in
      - textwidth=6.5in
      - showframe=false
    include-in-header: 
      - text: |
          \usepackage{placeins}
          \extrafloats{500}
          \maxdeadcycles=10000
          \usepackage{fontspec}
          \usepackage{multicol}
          \usepackage{hhline}
          \newlength\Oldarrayrulewidth
          \newlength\Oldtabcolsep
      - file: '`r system.file("files/ltx_ExtraLatexIncludes.tex",package="wtsQMD")`'
echo: false
message: false
warning: false
results: 'hide'
keep-md: true
keep-yaml: false
editor: source
editor_options: 
  chunk_output_type: console
concordance: true
params:
  setup: !expr 'system.file("files/qmd_setup.R",package="wtsQMD")'
  rdaAsmtSetup: "rda_AssessmentSetup.RData"
  dirAsmt: "~/Work/StockAssessments-Crab/Assessments/TannerCrab/2024-09_TannerCrab/AssessmentData/Data_Surveys_NMFS"
  testing: false
  reorderTables: false   #--issue with finding "range" of table values  (don't use)
  reorderFigures: false  #--issue with finding "range" of figure values (don't use)
---
<!-- IMPORTANT: if used as a child doc, all chunk labels must be unique within the overall document -->

<!-- 
  NOTEs: 
     * child_path$peek() gives path to current script folder.
     * before starting a child document, do 
         "child_path$push(file.path(child_path$peek(),rel_path))" first, 
         where rel_path is the relative path to the child
     * after a child document has finished, do "child_path$pop()" to return to current path value
-->

<!-- if not child doc, set up required objects -->
```{r}
#| label: REPT_setup
#| eval: !expr '!knitr::opts_knit$get("child")'
#| results: "asis"
  testing = params$testing;
  if (testing) cat(params$setup,"\n\n")
  source(params$setup);
  if (testing) cat("root = ",root,"\n\n")
  reorderTables  = params$reorderTables;
  reorderFigures = params$reorderFigures;
```

```{r}
#| label: setup_REPT
#| results: 'asis'
  require(ggplot2);
  require(kableExtra);
  require(tables);
  Sum = wtsUtilities::Sum;
  old_thm = ggplot2::theme_set(cowplot::theme_cowplot(font_size = 10) +
                               cowplot::background_grid() +
                               cowplot::panel_border());
  thm = wtsPlots::getStdTheme();
  options("readr.show_col_types"=FALSE);
  if (testing) cat("dirThs =",child_path$peek(),"\n\n")
  ##--NOTE: take out or modify the following as necessary
  if (!exists("s")){
    if (rstudioapi::isAvailable())
      fn = file.path(rstudioapi::getActiveProject(),"rda_ProjectSetup.RData");
    if (child_path$peek()!="")
      fn = file.path(child_path$peek(),"../rda_ProjectSetup.RData");
    #--for debugging: ;
    if (file.exists(fn)) s = wtsUtilities::getObj(fn);
  }
  ##--
```

\begin{center}
THIS INFORMATION IS DISTRIBUTED SOLELY FOR THE PURPOSE OF 
PREDISSEMINATION PEER REVIEW UNDER APPLICABLE INFORMATION QUALITY GUIDELINES. 
IT HAS NOT BEEN FORMALLY DISSEMINATED BY NOAA FISHERIES/ALASKA FISHERIES SCIENCE CENTER AND 
SHOULD NOT BE CONSTRUED TO REPRESENT ANY AGENCY DETERMINATION OR POLICY
\end{center}


# Introduction 

The next full assessment for the Tanner crab stock will be reviewed by the Crab Plan Team (CPT) in September 2025 and the NPFMC's (North Pacific Fishery Management Council) Science and Statistical Committee (SSC) in October 2025. The stock is on an annual cycle for assessment, with the last full assessment conducted in September 2024 [@TannerCrab2024]. 

This report addresses several topics, including new analyses, potential (bespoke) Tanner Crab Stock Assessment Model (v.2; TCSAM02) models for the Fall 2025 stock assessment, and work to develop a Generalized Model for Assessing Crab Stocks (GMACS) version of the Tanner crab assessment model. Among new analyses ([@sec-Analyses]), the AFSC's Shellfish Assessment Program (SAP) has developed an R package, `crabpack`, as a replacement to AKFIN Answers (https://akfin.psmfc.org) for obtaining crab-related survey data in a standard format. SAP staff requested that assessment authors test the package and compare results of data pulls using the package with data pulled using the authors' previous methods. Results of this comparison are presented in Section [-@sec-crabpack]. Model-based size compositions from the National Marine Fisheries Service (NMFS) Eastern Bering Seae (EBS) bottom trawl survey and estimated using the Vector Autoregressive Spatiotemporal (VAST; [@VAST2015]) `R` package are compared with standard design-based estimates in Section [-@sec-VAST-ZCs]. Finally, in response to an SSC request to compare spatial ranges and environmental conditions between juvenile cohorts that succeed and those that fail, Section [-@sec-SCsxs] provides a preliminary attempt to look at temperature and geographic conditions for two successful and one unsuccessful cohort of juvenile crab. Results from two models using the bespoke TCSAM02 framework are compared with results from the 2024 assessment assessment model in Section [-@sec-TCSAM02] to provide potential alternative models for the 2025 assessment. Finally, results from a GMACS model that attempts (but doesn't quite succeed) to duplicate the 2024 assessment model in the GMACS framework are presented in Section [-@sec-ModComps].

This report is organized into the following sections: Responses to previous CPT and SSC Comments (@sec-Resps), Analyses (@sec-Analyses), TCSAM02 model runs and results (@sec-TCSAM02), GMACS model run and comparison with the current assessment model (@sec-ModComps), Summary (@sec-Smry), and Acknowledgments (@sec-Acks).

<!-- # Responses to CPT and SSC Comments {#sec-Resps} -->
```{r sct_Resps, child=file.path(child_path$peek(),"q01_TannerCrab_ResponsesToComments2025.qmd")}
```

<!-- # "New" Data and Analyses {#sec-Analyses} -->
```{r sct_Analyses, child=file.path(child_path$peek(),"q02_Analyses.qmd")}
```

<!-- # TCSAM02 Models {#sec-TCSAM02} -->
```{r}
fldr = "../ModelRuns/ModelComparisons-TCSAM02";
child_path$push(file.path(child_path$peek(),fldr));
```
```{r sct_TCSAM02, child=file.path(child_path$peek(),"q01_TCSAM02_ModelComparisons.qmd")}
```
```{r}
fldr = child_path$pop();
```

<!-- # GMACS Models {#sec-GMACS} -->
```{r}
fldr = "../ModelRuns/ModelComparisons-TCSAM02-GMACS";
child_path$push(file.path(child_path$peek(),fldr));
```
```{r sct_GMACS, child=file.path(child_path$peek(),"q02_GMACS-TCSAM02_ModelComparisons.qmd")}
```
```{r}
fldr = child_path$pop();
```

# Summary {#sec-Smry}

In summary,

  * with regard to the `crabpack` R package developed by SAP, I
  
    - recommend using the full-precision carapace length measurements with the current length-weight regressions to calculate biomass from NMFS EBS survey abundance and size data.
    
    - recommend limiting the survey stations in 1979 to the 375 stations previously adopted as "standard" by the CPT for calculating crab survey abundance and biomass indices or size compositions using design-based methods.
    
    - recommend using data from all the available stations when calculating survey biomass and abundance indices or size compositions using model-based geostatistical (e.g., `VAST`, `sdmTMB`) methods.
    
  * with regard to using `VAST`-derived size compositions in the stock assessment, I recommend that a model using `VAST`-derived indices and size compositions be developed as an alternative model in 2026 pending further work to streamline the process of estimating and reviewing the results
  
  * with regard to "small crab success", I thank the SSC for the suggestion and hope the small overview given here provides some basis for further research on this topic, although further work needs to be done in coordination with SAP and perhaps led by analysts developing the Tanner crab ESP
  
  * with regard to alternative TCSAM02 models for the consideration as part of the 2025 stock assessment, I recommend including 25_02 as an alternative model in addition to the base. This model is attractive because using capture probability functions derived from the BSFRF data reduces overall model complexity by eliminating several selectivity/catchability-related parameters as well as the necessity to fit the BSFRF biomass indices and size compositions.
  
  * with regard to a GMACS alternative to the bespoke TCSAM02 model, substantial progress has been made on this: it feels like we're "almost there". I propose to continue to work on this over the summer and present an update on further progress at the 2025 stock assessment.

The author looks forward to discussions with the CPT and SSC regarding model choices for the September assessment and further refinements to address on a longer timescale.

# Acknowledgments {#sec-Acks}

The author would like to acknowledge Andre Punt (UW) and Matthieu Veron (previously at the AFSC-Seattle, now at the Institut Agro Rennes-Angers) for recent improvements to GMACS; Jon Richar (AFSC-SAP) for developing the VAST size compositions for Tanner crab; Shannon Hennessey (AFSC-SAP) and SAP for developing the `crabpack` R package; Cole Monnahan (AFSC-SSMA), Jim Ianelli (AFSC-SSMA), Andre, and other crab assessment authors for discussions on use and debugging of GMACS; and Cole for developing the ADMB "hess_step" routine and providing help with OSA residuals. I would also like to thank Lee Cronin-Fine (AFSC-SSMA) for providing an internal review of a draft version of this report.

<!-- references -->
```{r,eval=!knitr::opts_knit$get("child"),results='asis'}
  cat("# References {-}\n");
  cat("::: {#refs}\n");
  cat(":::\n\n");
```

<!-- tables, if not child doc and lstTbls is not empty -->
```{r}
#| label: tables_REPT
#| eval: !expr '!knitr::opts_knit$get("child")'
#| results: asis
  source(system.file("files/printTablesSectionFromList.R",package="wtsQMD"));
```

<!-- figures, if not child doc and lstFigs is not empty -->
```{r}
#| label: figures_REPT
#| eval: !expr '!knitr::opts_knit$get("child")'
#| results: asis
  source(system.file("files/printFiguresSectionFromList.R",package="wtsQMD"));
```
